Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-21 journal/article.tex
S: Commitment

@@

% ---------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}

>>>>

% Commitment (?)

A large change will inevitably require strong commitment. The agile model is
introduced because of problems in the old model, and therefore there will be
organizational issues uncovered during the transformation [P10]. People must not
be demoralized when facing challenges, and the determination to change must be
maintained [P8, P10]. It is not the agile model that has flaws, but it is
merely exposing problems in the organization [P10].
Ryan and Scudiere [P43] describe that management commitment was showing as
strong focus on certain agile practices that had been chosen as non negotiable,
and constant assessment that the practices work. The expectations were clearly
communicated to the teams, and constant assessment made it clear that change is
desired [P43].
A strong commitment from management will assure teams that the change is the
right thing [P11].

@@

\section{Discussion}
\label{sec:discussion}
